probKanren: A Simple Probabilistic extension for miniKanren

### 2021-07-25 paper/main.tex
Add more TODO notes

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Probabilistic programming is sometimes described as a generalisation
  of logic programming where instead of just returning a set of facts
  that answer a given query, we return a probability distribution over
  facts that answer a given query. But many contemporary probabilistic
  logic programming languages are not implemented as simple extensions
  of existing logic programming languages but instead involve their
  own unique implementations. Here we introduce probKanren, a simple
  extension to miniKanren that transforms
\end{abstract}

@@

@@

\begin{equation}
  x_n \sim f(x_n \mid x_{0:n-1}) \\
  w_n^{(k)} = \frac{g(x_n \mid x_{0:n})f(x_n \mid x_{0:n-1})}{q(x_n \mid x_{0:n-1})} \\
  W_n^{(k)} = W_{n-1}^{(k)} w_n^{(k)}
\end{equation}

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Probabilistic programming is sometimes described as a generalisation
  of logic programming where instead of just returning a set of facts
  that answer a given query, which return a probability distribution over
  facts that answer a given query. But many contemporary probabilistic
  logic programming languages are not implemented as simple extensions
  of existing logic programming languages but instead involve their
  own unique implementations. Here we introduce probKanren, a simple
  extension to miniKanren that transforms
\end{abstract}

@@

Define terms, goals, and substitutions here

@@

\begin{eqnarray}
  x_n &\sim& f(x_n \mid x_{0:n-1}) \\
  w_n^{(k)} &=& \frac{g(x_n \mid x_{0:n})f(x_n \mid x_{0:n-1})}{q(x_n \mid x_{0:n-1})} \\
  W_n^{(k)} &=& W_{n-1}^{(k)} w_n^{(k)}
\end{eqnarray}

@@

\section{Grammar and Definitions}

Define distributional clauses here
